---
title: "Color analysis"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d()
scale_fill_discrete = scale_fill_viridis_d()
```

```{r}
load("tidy_data.Rdata")

n_color = 
  tidy_data %>%
  ggplot(aes(x = ncolor, fill = ncolor)) +
  geom_bar() + 
  labs(
  title = "Number of dog colors",
  x = "Number of color",
  y = "Count") + 
  theme(legend.position = 'none')
```

This barplot shows the distribution of number of dog color in Allegheny County in PA -- the pure color dog have the largest number and mixed of more than 3 colors have the least.

```{r}
color_all = 
  tidy_data %>% 
  count(color) %>% 
  arrange(desc(n)) %>% 
  top_n(10) %>%
  ggplot(aes(x = reorder(color, n), y = n,  fill = n, alpha = 0.8)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(
  title = "Top 10 famous dog colors",
  x = "Count",
  y = "Color") + 
  theme(legend.position = 'none')

color_1 = 
  tidy_data %>% 
  filter(ncolor == "1") %>% 
  count(color) %>% 
  arrange(desc(n)) %>% 
  top_n(5) %>%
  ggplot(aes(x = reorder(color, n), y = n,  fill = n, alpha = 0.8)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(
  title = "Top 5 famous colors for pure color dogs",
  x = "Count",
  y = "Color") + 
  theme(legend.position = 'none')

color_2 = 
  tidy_data %>% 
  filter(ncolor == "2") %>% 
  count(color) %>% 
  arrange(desc(n)) %>% 
  top_n(5) %>%
  ggplot(aes(x = reorder(color, n), y = n,  fill = n, alpha = 0.8)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(
  title = "Top 5 famous colors for two-color dogs",
  x = "Count",
  y = "Color") + 
  theme(legend.position = 'none')

color_3 = 
  tidy_data %>% 
  filter(ncolor == "3+") %>% 
  mutate(color = recode(color, `MULTI//` = "MULTI", `TRI-COLOR//` = "TRI-COLOR")) %>% 
  count(color) %>% 
  arrange(desc(n)) %>% 
  top_n(5) %>%
  ggplot(aes(x = reorder(color, n), y = n, fill = n, alpha = 0.8)) +
  geom_bar(stat="identity") +
  coord_flip() +
  labs(
  title = "Top 5 famous colors for mixed color dogs",
  x = "Count",
  y = "Color") + 
  theme(legend.position = 'none')

popular_color = (color_all + color_1) / (color_2 + color_3)
```

These plots show several famous color in Allegheny County, including black, brown, white, etc., and the most popular color is black.

```{r}
breed_color = 
  tidy_data %>% 
  ggplot(aes(x=ncolor, group = breed_type)) + 
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  scale_y_continuous(labels=scales::percent) +
  geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.5) +
  facet_grid(. ~ breed_type) + 
  theme(legend.position = 'none') +
  labs(
  title = "Breed type proportion according to ncolor",
  x = "ncolor",
  y = "Proportion")

license_ncolor = 
  tidy_data %>% 
  ggplot(aes(x=ncolor, group = license_type)) + 
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  scale_y_continuous(labels=scales::percent) +
  geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.5) +
  facet_grid(. ~ license_type) + 
  theme(legend.position = 'none') +
  labs(
  title = "License type proportion according to ncolor",
  x = "ncolor",
  y = "Proportion")
```

These graphs indicate that there are no significant correlation between number of color and license type/breed type of the dog. The distributions are similar in each group.

```{r}
license_color = 
  tidy_data %>% 
  filter(color %in% c("BLACK", "BROWN", "WHITE/BLACK", "BLACK/BROWN", "WHITE",
                      "WHITE/BLACK/BROWN", "WHITE/BROWN", "BRINDLE", "GOLD", "SPOTTED")) %>% 
  ggplot(aes(x=color, group = license_type)) + 
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  scale_y_continuous(labels=scales::percent) +
  geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.5) +
  facet_grid(. ~ license_type) +
  coord_flip() + 
  theme(legend.position = 'none') +
  labs(
  title = "Distribution of dog license type with top 10 popular colors.",
  x = "ncolor",
  y = "Proportion")
```

This graph shows the distribution of dog license type with top 10 popular colors. There are no obvious regular pattern.

