---
title: 'Brooklyn: Eviction Rates Over Time'
output: github_document
  
---

```{r setup, include=FALSE}



```


Neighborhoods Over Time
===================================== 

Column {.sidebar}
-----------------------------------------------------------------------


```{r for_sidebar}



```

Column {.tabset}
-----------------------------------------------------------------------

### Brooklyn 2000-2016

```{r spaghetti_map}


# Spaghetti plot over time




```

### Description

The line plot illustrates the eviction rates from 2000 to 2016 across 51 distinct Brooklyn neighborhoods. Users can compare neighborhoods side-by-side and visualize differences in how this parameter has changed over time throughout Brooklyn.

**Not all neighborhoods have complete eviction data for each year.**

Map Over Time: Census Tract
===================================== 

Column {.sidebar}
-----------------------------------------------------------------------

```{r for_sidebar_2}
# Create slider widget


```

Column {.tabset}
-----------------------------------------------------------------------

### Eviction Rate Over Time Map

```{r map_eviction}


```

### Description

This map displays the census-tract level eviction rates across Brooklyn from the years 2000 to 2016. 
