---
title: "Validation Date of Lifetime Dog Licenses in Allegheny County"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(ggpubr)
library(ggpmisc)
library(ggplot2)

knitr::opts_chunk$set(
	echo = FALSE,
	warning = FALSE,
	fig.width = 12, 
  fig.height = 8,
	fig.path='Figs_Valid_date/',
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

load("tidy_data.Rdata")
```

# About Valid date

Data about the validation date contains the year and the time of validation date. We analyze the the trend of lifetime dog licenses over 17 years and the preferred time for people obtaining the lifetime licenses. 

# Analysis on Trend over Years from 2003 to 2020

```{r}
plot_valid_year =
 tidy_data %>%
 group_by(valid_year) %>%
 count(valid_year) %>%
ggplot(
 aes(x = valid_year, y = n, fill = valid_year))+
  geom_point()+
  geom_smooth(formula = y ~ x, method = loess, se = F)+
 labs(
  x = "Year of Valid Date",
    y = "Number of Lifetime Licenses",
    title = "Number of Lifetime Licenses from 2003 to 2020 "
 )
plot_valid_year
```

From the plot above, we can see there existing a linear relationship between the the number of the total lifetime dog licenses and the year of valid year from 2003 to the 2019. However, in 2020, the number of the lifetime licenses decreased a little, which might result from the Covid-19. Therefore, in this case, we have the graph below to show the linear equation without the effect of 2020:

```{r}
lm_valid_year =
 tidy_data %>%
 group_by(valid_year) %>%
 count(valid_year) %>%
 filter(valid_year != 2020) %>%
ggplot(
 aes(x = valid_year, y = n, fill = valid_year))+
  geom_point()+
  geom_smooth(formula = y ~ x, method = loess, se = TRUE, level = 0.95) +
  stat_poly_eq(formula = y ~ x,
                eq.with.lhs = "italic(hat(y))~`=`~",
                aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
                parse = TRUE, size = 10) +
 labs(
  x = "Year of Valid Date",
    y = "Number of Lifetime Licenses",
    title = "Number of Lifetime Licenses from 2003 to 2019"
 )
lm_valid_year
```

Since the R square is 0.99, we can conclude that the linear equation is robust and we can use it to predict the the number of total dog lifetime licenses in the future without the effects from Covid-19. The 95% confidence interval includes almost all values from 2003 to 2019. 

# Analysis on the Prefered Time to Obtain a Dog Lifetime License

```{r}
plot_valid_time =
 tidy_data %>%
 drop_na(valid_time) %>%
 group_by(valid_time) %>%
 count(valid_time) %>%
ggplot(
 aes(x = valid_time, y = n, fill = valid_time))+
 geom_bar(stat = "identity")+
 labs(
  x = "Time of Valid Date",
    y = "Number of Lifetime Licenses",
    title = "Prefered Time to Obtain Dog Lifetime Licenses")
plot_valid_time
```

From the bar chart above, people tend to obtain the lifetime licenses on PM rather than AM. The people obtain the lifetime licenses is nearly double the people on AM. 
.